Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed the analysis of country and continent most studied as they can be gotten from the table of counts

#Print the results
knitr::kable(continents_studied_by_count, 
             caption = 'Number of studies per country'
             )
```

### Country most studied
```{r echo=FALSE}
countries_studied_most <- countries_studied_by_count %>%
    filter(country_studied != 'none') %>%
    filter(num_of_studies == max(num_of_studies))

#Print the result as a table
knitr::kable(countries_studied_most,
             col.names = c('Country',
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Most studied country'
             )
```

### Continent most studied
```{r echo=FALSE}

continent_studied_most <- continents_studied_by_count %>%
    dplyr::filter(continent_studied != 'none') %>%
    filter(num_of_studies == max(num_of_studies))

#Print the result as a table
knitr::kable(continent_studied_most,
             col.names = c('Continent',
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Most studied continent'
             )
```

>>>>

#Print the results
knitr::kable(continents_studied_by_count, 
```
